\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-09-20 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added Ainsworth
renamed CUBIT directory to CUBIT_GEOCUBIT

It has very good accuracy and convergence properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08,MeStTh12}.
The spectral element approach admits spectral rates of convergence
and allows exploiting $hp$-convergence schemes. It is also very well
suited to parallel implementation on very large supercomputers \citep{KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10}
as well as on clusters of GPU accelerating graphics cards \citep{KoMiEr09,KoErGoMi10,Kom11}.
Tensor products inside each element can be optimized to reach very
high efficiency \citep{DeFiMu02}, and mesh point and element numbering
can be optimized to reduce processor cache misses and improve cache
reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D)
or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06}
as well as mixed meshes, although with increased cost and reduced
accuracy in these elements, as in the discontinuous Galerkin method.\\

@@

After the block definitions are done, you export the mesh using the
script \texttt{cubit2specfem3d.py} provided in each of the example
directories (linked to the common script \texttt{CUBIT/cubit2specfem3d.py}). If the export was successful, you should find the following
files in a subdirectory \texttt{MESH/}:
\begin{description}
\item [{absorbing\_cpml\_file}] \textbf{(only needed in case of C-PML absorbing
conditions)} Contains on the first line the total number of C-PML
spectral elements in the mesh, and then on the following line the
list of all these C-PML elements with two numbers per line: first
the spectral element number, and then a C-PML flag indicating to which
C-PML layer(s) that element belongs, according to the following convention:

>>>>

It has very good accuracy and convergence properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08,AiWa09,AiWa10,MeStTh12}.
The spectral element approach admits spectral rates of convergence
and allows exploiting $hp$-convergence schemes. It is also very well
suited to parallel implementation on very large supercomputers \citep{KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10}
as well as on clusters of GPU accelerating graphics cards \citep{KoMiEr09,KoErGoMi10,Kom11}.
Tensor products inside each element can be optimized to reach very
high efficiency \citep{DeFiMu02}, and mesh point and element numbering
can be optimized to reduce processor cache misses and improve cache
reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D)
or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06}
as well as mixed meshes, although with increased cost and reduced
accuracy in these elements, as in the discontinuous Galerkin method.\\

@@

After the block definitions are done, you export the mesh using the
script \texttt{cubit2specfem3d.py} provided in each of the example
directories (linked to the common script \texttt{CUBIT\_GEOCUBIT/cubit2specfem3d.py}). If the export was successful, you should find the following
files in a subdirectory \texttt{MESH/}:
\begin{description}
\item [{absorbing\_cpml\_file}] \textbf{(only needed in case of C-PML absorbing
conditions)} Contains on the first line the total number of C-PML
spectral elements in the mesh, and then on the following line the
list of all these C-PML elements with two numbers per line: first
the spectral element number, and then a C-PML flag indicating to which
C-PML layer(s) that element belongs, according to the following convention:
